\documentclass[10pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\author{AKOLL CARLTON NOEL}
\title{LITERATURE REVIEW ON ANDROID APPLICATIONS.}
\begin{document}
\maketitle

Technology has grown and evolved so rapidly over the past decade and we as humans have become so reliant on it in that it’s become part of our daily our lives. The best example to show just how reliant we have become on technology is the smartphone. the first smartphone was introduced in 2007 by Apple and now in 2018 over 36 percent of people in the world own a smartphone \cite{r1} . \\
In the United States alone, 64 percent of the population uses a smartphone on a daily basis \cite{r2} . Smartphones are built using a variety of operating systems and today, there are at least five important platforms (iPhone, Android, Blackberry, Windows Phone, Symbian) \cite{r3}  however a large portion of the mobile markets in the world are currently iPhone and Android \cite{r4} .\\

Focusing on Android since it’s the mostly widely used the world right now, nowadays most of student have their own android phones they commonly use for internet in order to search some projects and homework. Right now technologies have enhanced its mechanism not only for searching but also for learning and updating some activities that was already program in schools. Searching and updating some of those activities outside the school is a little bit hard or let say it is so hassle to bring laptop outdoor when you’re in hurry.\\

With the constant use of android smartphones, a great deal of android applications have been developed that serve a great number of purposes. One of the system that we are pursuing that can help students like us, is the Android APS for Students Affair School Calendar this application includes the following schedule of the particular day. This android application you don’t need to go to school Just to know what’s happening, you Just turn on your mobile phones and Just read the following details. Statement of the problem:\\
1.Why they would choose this kind of application?\\
 2. How they could know if they were updated to the events in school?\\
  3. When they well know if there’s an event in school?
From \cite{r5} .\\
 This in-depth book provides the concepts and code that is needed to start building smartened applications with Android programming environment. Android Application Development introduces the environment including the operating system and SAD, and provides working examples with thorough explanations to demonstrate Android’s architectural features and Apish.
 \bibliographystyle{unsrt} 
\bibliography{Ref}

\end{document}